Issues with Dynamical Measurements Across the Disk

### 2019-02-26 paper/ms.tex
Add contrast to chemical solar neighborhood

\subsection{The size of the Solar neighborhood} \label{sssec:neighborhood}
Given a local coordinate system, the amplitude and characteristic length scale
of the density fluctuations in the Galactic disk will determine how far this
system can be extended before introducing $\mathcal{O}(1)$ systematic errors
in the computation of actions for thin-disk stars. We consider this a
criterion for the region around the Sun where the analysis of the action-space
distribution of stars on quasi-circular orbits, and therefore the epicyclic
approximation, can be expected to be valid. This leads to a somewhat
dynamically motivated definition of the ``solar neighborhood.''

>>>>

\subsection{The size of the Solar neighborhood} \label{sssec:neighborhood}
Given a local coordinate system, the amplitude and characteristic length scale
of the density fluctuations in the Galactic disk will determine how far this
system can be extended before introducing $\mathcal{O}(1)$ systematic errors
in the computation of actions for thin-disk stars. We consider this a
criterion for the region around the Sun where the analysis of the action-space
distribution of stars on quasi-circular orbits, and therefore the epicyclic
approximation, can be expected to be valid. This leads to a somewhat
dynamically motivated definition of the ``solar neighborhood.'' Since the
motivation may be different for defining the solar neighborhood in e.g.
studies of the chemical distribution of the Galaxy, we propose the phrase
``dynamical solar neighborhood.''
